---
title: Goals
description: "This page is a collation of my goals (prospective) and achievements (retrospective). The purpose is to be something of a reminder of both how far I have come and what I am working towards. My vague cutoff is from my university days onwards."
# Enable banner style title blocks
title-block-banner: "#4C4C4B"
title-block-style: default
execute:
  echo: false
  warning: false
format:
  html:
    page-layout: full
---


```{r setup}
source("../scripts/reactable-theming.R")
library(googlesheets4)
library(dplyr)
library(glue)
library(purrr)
library(reactable)
library(reactablefmtr)
library(tippy)
library(htmltools)
library(scales)

```


::: callout-tip
## Non-linearity

I would also like to emphasise the non-linearity and compounding nature of personal progress. As such, I have also included some *roadblocks* and *failures* I have experience along the way.

This is my attempt to run counter to what one might see on a resume or social media (predominately successes and seldom failures). I am also doing this as a reminder that:

-   Not all ventures succeed (and this is okay).
-   It is from failures that we often learn the most.
-   Without risking failure, we will never dare to do anything bold.
:::

# Summary Tables

The tables below are split into tabs by category (*Study*, *Professional*, *Personal Projects* and *Extracurricular*). Each table row is a different project. Click the arrow to the left of each row, to expand each project into a table with my goals. If the 🖱 ️symbol appears in a cell, then it has a tooltip which you can view by hovering over it with your mouse.


```{r}
display_text_as_tooltip <- function(value, index) {
  

  if(is.na(value)) {
    return("")
  } else {
    return(tippy("Hover for detail", interactive = TRUE, tooltip = value))
    
  }
  
}
```

```{r get data}
ss <- gs4_get("https://docs.google.com/spreadsheets/d/1kRK0zWsGz7GOHhtWSaV_9SlZ2zRxns_pVEh4YMJtsLQ/edit#gid=0")
goals_tb <- read_sheet(ss, sheet = "Goals") |> 
  filter(!is.na(project)) |> 
  relocate(goal_completed_flag, .before = goal_start_date)
projects_tb <- read_sheet(ss, sheet = "Projects") |> 
  filter(!is.na(project)) |> 
  select(-c("completion_date (formulaic)", "completion_date (manual)"))
categories_tb <- read_sheet(ss, sheet = "Categories")



# combined_tb <- left_join(projects_tb, goals_tb, by = "project") |> 
#   left_join(categories_tb, by = "category") |> 
#   select(category, info1,  info2, completed_flag, goal, goal_completed_flag)

```

```{r}
goals_table_category <- function(category_label) {
  categories_tb |>
      filter(category == category_label) -> categories_tb_filtered
  
  info1_label <- categories_tb_filtered$info1_label  
  info2_label <- categories_tb_filtered$info2_label  

  
  renaming_list <- `names<-`(c("info1", "info2"), c(info1_label, info2_label))
  
  projects_tb_filtered <- projects_tb |> 
    filter(category == category_label) |> 
    select(-category) |> 
    rename(all_of(renaming_list))
  
  info_col_spec <- list(
    colDef(
      cell = \(cell_value, row_index, column_name) {
        description <- projects_tb_filtered[row_index, "description"][[1]]
        if(is.na(description)) {
          cell_value
          } else {
            tippy::tippy(paste(cell_value, "🖱"), paste("<b>More Details</b></br>", description))
          }
        }
      ),
    colDef(
      )
  ) |> 
    `names<-`(value = c(info1_label, info2_label))
  
  

  
  projects_tb_filtered |> 
    reactable_themed(
      details = function(index) {
        .project <- projects_tb_filtered$project[[index]]
        goals_tb_filtered <- goals_tb |>
          filter(project == .project)
        goals_tb_filtered |>
          reactable_themed(
            outlined = TRUE,
            columns = list(
              project = colDef(show = FALSE),
              goal_completed_flag = colDef(
                name = "Completion",
                cell = \(cell_value, row_index, column_name) {
                  if(cell_value) {
                    render_text <- "️✅"
                  } else {
                    in_progress <- goals_tb_filtered[row_index, "in_progress"][[1]]
                    if(in_progress) {
                      render_text <- "🟡"
                    } else {
                      render_text <- "❌"
                    }
                  }
                  road_blocks <- goals_tb_filtered[row_index, "road_blocks"][[1]]
                  if(is.na(road_blocks)) {
                    render_text
                  } else {
                    tippy::tippy(paste(render_text, "🖱"), paste("<b>Road Block</b></br>", road_blocks))
                  }
              }),
              goal_description = colDef(show = FALSE),
              goal_start_date = colDef(name = "Date Started", format = colFormat_aus(date = TRUE)),
              goal_completion_date = colDef(name = "Date Completed", format = colFormat_aus(date = TRUE)),
              in_progress = colDef(show = FALSE),
              road_blocks = colDef(show = FALSE),
              link = colDef(
                name = "Link",
                cell = \(cell_value, row_index, column_name) {
                  if(is.na(cell_value)) {
                    ""
                  } else {
                    tags$a(target = "_blank", href = cell_value, "🔗")
                  }
                }),
              goal = colDef(
                name = "Goal",
                cell = \(cell_value, row_index, column_name) {
                  goal_description <- goals_tb_filtered[row_index, "goal_description"][[1]]
                  if(is.na(goal_description)) {
                    cell_value
                    } else {
                      tippy::tippy(paste(cell_value, "🖱"), paste("<b>More Details</b></br>", goal_description))
                    }
                  }
                )
              )
            ) |> 
          div(style = "padding: 1rem")
      },
      pagination = FALSE,
      columns = list(
        project = colDef(show = FALSE),
        start_date = colDef(name = "Date Started", format = colFormat_aus(date = TRUE)),
        completion_date = colDef(name = "Date Completed", format = colFormat_aus(date = TRUE)),
        description = colDef(show = FALSE),
        completed_flag = colDef(
          name = "Status",
          cell = \(cell_value, row_index, column_name) {
            if(cell_value) {
              "️✅"
            } else {
              completion <- projects_tb_filtered[row_index, "goal_completion"][[1]]
              if(completion > 0) {
                paste("🟡", scales::percent(completion))
              } else {
                "❌"
              }
              
            }
        }),
        goal_count = colDef(show = FALSE),
        goal_achieved = colDef(show = FALSE),
        goal_partial = colDef(show = FALSE),
        goal_completion = colDef(show = FALSE),
        completed_flag = colDef()
      ) |> 
        c(info_col_spec)
      )
  
}
```

<!-- :::: {.column-screen} -->



::: panel-tabset
## Study

```{r}
goals_table_category("Study")

```

## Professional

```{r}
goals_table_category("Professional")
```

## Personal Projects

```{r}
goals_table_category("Personal Projects")
```

## Extracurricular Activities

```{r}
goals_table_category("Extracurricular")
```
:::

<!-- :::: -->


## Table Legend

Below is a legend for the *Status* and *Completion* fields.

```{r}
tribble(
  ~"Symbol", ~"Meaning",
  "✅", "Complete",
  "🟡", "In Progress",
  "❌",  "Not Started"
) |> 
  reactable_themed(fullWidth = FALSE, width = 250)
```


