---
Title: Goals
execute:
  echo: false
  warning: false
format:
  html:
    page-layout: full
title-block-banner: true
---

# Goals


This page is a collation of my goals (prospective) and achievements (retrospective). The purpose is to be something of a reminder of both how far I have come and what I am working towards. My vague cutoff is from my university days onwards.


::: {.callout-tip}

## Non-linearity

I would also like to emphasise the non-linearity and compounding nature of personal progress. As such, I have also included some *roadblocks* and *failures* I have experience along the way.

This is my attempt to run counter to what one might see on a resume or social media (successes only). I am also doing this as a reminder that:

* Not all ventures succeed (and this is okay).
* It is from failures that we often learn the most.
* Without risking failure, we will never dare to do anything bold.

:::






```{r setup}
source("../scripts/reactable-theming.R")
library(googlesheets4)
library(dplyr)
library(glue)
library(reactable)
library(reactablefmtr)
library(tippy)
library(htmltools)


```



```{r}
display_text_as_tooltip <- function(value, index) {
  

  if(is.na(value)) {
    return("")
  } else {
    return(tippy("Hover for detail", interactive = TRUE, tooltip = value))
    
  }
  
}
```


```{r get data}
ss <- gs4_get("https://docs.google.com/spreadsheets/d/1kRK0zWsGz7GOHhtWSaV_9SlZ2zRxns_pVEh4YMJtsLQ/edit#gid=0")
goals_tb <- read_sheet(ss, sheet = "Goals") %>% 
  filter(!is.na(goal))
sub_goals_tb <- read_sheet(ss, sheet = "Sub-Goals") %>% 
  filter(!is.na(goal))

combined_tb <- left_join(goals_tb, sub_goals_tb, by = "goal") %>% 
  select(category, goal_label, start_date, completion_date, sub_goal, sub_goal_start_date, sub_goal_completion_date, sub_goal_description, sub_goal_completed_flag) %>% 
  arrange(category, start_date) %>%
  select(-start_date, -completion_date) 

```


```{r}
combined_tb %>% 
  reactable_themed(
    groupBy = c("category", "goal_label"),
    defaultExpanded = FALSE,
    columns = list(
      category = colDef(
        name = "Category"
        # ,
        # style = reactable_merged("category")
        ),
      goal_label = colDef(
        name = "Goal"
        # ,
        # style = reactable_merged("goal_label")
        ),
      sub_goal = colDef(
        name = "Sub-Goal"
        ),
      sub_goal_start_date = colDef(
        name = "Start Date",
        aggregate = "min",
        format = colFormat(date = TRUE)
      ),
      sub_goal_completion_date = colDef(
        name = "Completion Date",
        aggregate = "max",
        format = colFormat(date = TRUE)
      ),
      sub_goal_description = colDef(
        name = "Description",
        cell = display_text_as_tooltip
      ),
      sub_goal_completed_flag = colDef(
        name = "Completed"
      )
      ),
    pagination = FALSE
    )


```

